### 2013-07-18 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding more to chapter summaries

\begin{itemize}
\item Forward-Automated Newton-MCSA (FANM), a new inexact Newton
  method based on Monte Carlo synthetic acceleration, has been
  developed
\item The FANM method has been incorporated into the Drekar production
  multiphysics code
\item The FANM method has been verified to produce the same solutions
  as a production Newton-Krylov method for two benchmark problems for
  the Navier-Stokes equations in different flow regimes
\item The FANM method has better iterative performance than the
  Newton-Krylov method for convection dominated problems, converging
  in fewer linear solver iterations with the same preconditioning for
  high and lower Rayleigh numbers
\item The Newton-Krylov method has better iterative performance than
  the FANM method for flow dominated by interial forces, converging in
  fewer linear solver iterations with the same preconditioning
\item The spectral radius convergence restriction on MCSA was observed
  to be a signficant hinderance by preventing solutions to forced flow
  problems at high Reynolds numbers
\item Explict algebraic preconditioning of MCSA creates FANM run times
  $O(100)$ slower than the Newton-Krylov solver
\item More Monte Carlo histories at every FANM iteration can reduce
  the number of linear and nonlinear iterations required to converge
  the problem
\end{itemize}

>>>>

\begin{itemize}
\item Forward-Automated Newton-MCSA (FANM), a new inexact Newton
  method based on Monte Carlo synthetic acceleration, has been
  developed
\item The FANM method has been incorporated into the Drekar
  multiphysics production code base developed at Sandia National
  Laboratories
\item The FANM method has been verified to produce the same solutions
  as a production Newton-Krylov method for two benchmark problems for
  the Navier-Stokes equations in different flow regimes
\item The FANM method has better iterative performance than the
  Newton-Krylov method for convection dominated problems, converging
  in fewer linear solver iterations with the same preconditioning for
  high and low Rayleigh numbers
\item The Newton-Krylov method has better iterative performance than
  the FANM method for flow dominated by interial forces, converging in
  fewer linear solver iterations with the same preconditioning
\item The spectral radius convergence restriction on MCSA was observed
  to be a signficant hinderance by preventing solutions to forced flow
  problems at high Reynolds numbers
\item Explict algebraic preconditioning of MCSA creates FANM run times
  $O(100)$ slower than the Newton-Krylov solver
\item More Monte Carlo histories at every FANM iteration can reduce
  the number of linear and nonlinear iterations required to converge
  the problem
\item With future optimization, reactor accident scenario analyses
  that rely on convection dominated transport could experience
  improved time to solution with FANM given the improved iterative
  performance for problems of this type
\end{itemize}

### 2013-07-18 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding more to chapter summaries

\begin{itemize}
\item MCSA can be effectively parallelized using domain decomposition
\item The leakage fraction of stochastic histories from a parallel
  subdomain can be quantified analytically using algebraic quantities
\item The multiple-set overlapping-domain (MSOD) parallel algorithm
  for particle transport has been adapted to parallelize MCSA
\item MCSA parallelized with MSOD was verified to produce the same
  results for solutions to the neutron diffusion equation as
  production Krylov methods
\item Strong scaling studies were performed with up to 65,536 cores
  and weak scaling studies were performed with up to 131,072 cores
\item MCSA scales comparably to production Krylov methods on the Titan
  Cray XK7 leadership class machine
\item Overlap in small quantities determined analytically by random
  walk length can provide parallel efficiency boosts of a few percent
  in strong scaling cases but is ineffective in weak scaling cases
\item Multiple sets will never boost parallel efficienicies in both
  weak and strong scaling cases due to additional communication
  overhead
\item Multiple sets offers a means to reduce time to solution by
  solving a multiple copies of the original problem and combining the
  solutions using superposition
\item MCSA is most efficient used in parallel as a stochastic
  realization of an additive Schwarz method
\end{itemize}

>>>>

\begin{itemize}
\item MCSA can be effectively parallelized using domain decomposition
\item The leakage fraction of stochastic histories from a parallel
  subdomain can be quantified analytically using algebraic quantities
\item The multiple-set overlapping-domain (MSOD) parallel algorithm
  for particle transport has been adapted to parallelize MCSA
\item MCSA parallelized with MSOD was verified to produce the same
  results for solutions to the neutron diffusion equation as
  production Krylov methods
\item Strong scaling studies were performed with up to 65,536 cores
  and weak scaling studies were performed with up to 131,072 cores on
  the Titan Cray XK7 leadership class machine at Oak Ridge National
  Laboratory
\item MCSA scales favorably compared to production Krylov methods for
  both strong and weak scaling cases
\item Overlap in small quantities determined analytically by random
  walk length can provide parallel efficiency boosts of a few percent
  in strong scaling cases but is ineffective in weak scaling cases
\item Multiple sets will never boost parallel efficienicies in both
  weak and strong scaling cases due to additional communication
  overhead from added reduction operations
\item Multiple sets offers a means to reduce time to solution by
  solving a multiple copies of the original problem and combining the
  solutions using superposition
\item MCSA is most efficient used in parallel as a stochastic
  realization of an additive Schwarz method
\item With future optimization, large scale reactor analyses in which
  the transport operator is fully formed (e.g. the $SP_N$ equations)
  could experience improved time to solution on leadership-class
  machines with MCSA given the improved scaling performance
\end{itemize}

### 2013-07-18 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding more to chapter summaries

\begin{itemize}
\item MCSA can be used to solve the asymmetric system generated by the
  multigroup $SP_N$ equations
\item Simple Jacobi-based preconditioning reduces the spectral radius
  of the $SP_N$ system below unity, however, this is not sufficient
  for MCSA convergence
\item As the spectral radius approaches unity, MCSA was demonstrated
  to break down with more stochastic histories required for
  convergence and more CPU time required per history
\item Advanced algebraic preconditioning strategies were applied to
  the $SP_N$ equations with ILUT chosen for subsequent investigations
\item The reduced domain approximation was required to mitigate the
  memory constraints of the explicit preconditioning strategy
\item MCSA relaxation parameters were developed an observed to enhance
  the time to solution for the fuel assembly problem
\item MCSA was verified to produce the same flux distribution and
  k-eigenvalue for the fuel assembly as production Krylov methods
\item MCSA was observed to converge in fewer iterations per eigenvalue
  iteration than GMRES for the fuel assembly problem and more then
  Bi-CGStab
\item The explicit preconditioning strategy creates MCSA runtimes
  $O(100)$ larger than the production Krylov methods
\end{itemize}

>>>>

\begin{itemize}
\item MCSA can be used to solve the asymmetric system generated by the
  multigroup $SP_N$ equations
\item MCSA has been incorporated into the Exnihilo neutronics
  production code base developed at Oak Ridge National Laboratory
\item Simple Jacobi-based preconditioning reduces the spectral radius
  of the $SP_N$ system below unity, however, this is not sufficient
  for MCSA convergence
\item As the spectral radius approaches unity, MCSA was demonstrated
  to break down with more stochastic histories required for
  convergence and more CPU time required per history
\item Advanced algebraic preconditioning strategies were applied to
  the $SP_N$ equations to obtain convergence with ILUT chosen for
  subsequent investigations
\item The reduced domain approximation was required to mitigate the
  memory and performance constraints of the explicit preconditioning
  strategy although both remain significant obstacles
\item MCSA relaxation parameters were developed an observed to enhance
  the time to solution for the fuel assembly problem
\item MCSA was verified to produce the same flux distribution and
  k-eigenvalue for the fuel assembly as production Krylov methods
\item MCSA was observed to converge in fewer iterations per eigenvalue
  iteration than GMRES for the fuel assembly problem and more then
  Bi-CGStab
\item The explicit preconditioning strategy creates MCSA runtimes
  $O(100)$ larger than the production Krylov methods for the fuel
  assembly problem
\end{itemize}
